Optimal Light Curve Attitude Inversion with Measurement Noise: Two Case Studies

### 2025-02-18 paper.tex
added some eqs

% introduce this option for the ESA publications style

@@

\section{General Specifications}

@@

>>>>

\usepackage{bm} % for bold math
\usepackage{mathtools} % for \prescript
\newcommand{\vctr}[1]{\bm{#1}}
\newcommand{\unitv}[1]{\hat{\vctr{#1}}}
\newcommand{\preup}[1]{\prescript{#1}{}{}}
\newcommand{\rf}[1]{\mathcal{\MakeUppercase{#1}}}
\newcommand{\dcm}[1]{\left[\rf{#1}\right]}
\newcommand{\vrf}[2]{\preup{\rf{#1}}\vctr{#2}}
\newcommand{\mbar}[0]{\;\middle|\;}
\newcommand{\prf}[1]{\preup{\rf{#1}}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\newcommand{\matcp}[1]{\left[#1 \times\right]}
\newcommand{\rthree}[0]{$\mathbb{R}^3$\:}
\newcommand{\sthree}[0]{$\mathbb{S}^3$\:}
\newcommand{\sothree}[0]{$SO_3$}
\newcommand{\pogslla}[0]{$32.900^\circ \textrm{ N}, -105.533^\circ \textrm{ W} \textrm{ }$}

\newcommand{\fighuge}[0]{1.0\textwidth}
\newcommand{\figbig}[0]{0.8\textwidth}
\newcommand{\figmed}[0]{0.6\textwidth}
\newcommand{\figsmall}[0]{0.4\textwidth}

\newcommand{\subfigmed}[0]{0.4\textwidth}
\newcommand{\subfigsm}[0]{0.29\textwidth}
\newcommand{\subfigbig}[0]{0.43\textwidth}

\DeclareMathOperator{\atantwo}{atan2}
\DeclareMathOperator{\fl}{floor}

@@

\section{Introduction}

@@

\section{Inversion Method}

\begin{equation} \label{eq:nll_loss}
  f_\text{NLL}(\hat{\vctr{S}}, \vctr{S}) = \frac{1}{m}\sum_{k=1}^{m}\left[\ln\sigma_k + \frac{1}{2}\left(\frac{S_k - \hat{S}_k}{\sigma_k}\right)^2 \right].
 \end{equation}

\begin{equation}
  \vctr{x} = \begin{bmatrix} 
  p_1 & p_2 & p_3 & \omega_1 & \omega_2 & \omega_3 & \frac{J_y}{J_x} & \frac{J_z}{J_x}
  \end{bmatrix}^T.
 \end{equation}

\begin{align}
  \vctr{\dot{\sigma}} &= \frac{1}{4} \left[ \left(1 - \vctr{p} \cdot \vctr{p}\right) + 2\vctr{p} \times \vctr{\omega} + 2 \left(\vctr{\omega} \cdot \vctr{p} \right)\vctr{p} \right] \label{eq:mrp_kde} \\
  \vctr{\dot{\omega}} &= J^{-1} \left[ \left(J \vctr{\omega}\right) \times \vctr{\omega} + \vctr{M}\right] \label{eq:rbtf_dynamics}
\end{align}

\begin{equation}
  \vctr{p}'' = \frac{\left(1-\norm{\sigma'}^2\right)\vctr{p} - \left(1-\norm{\vctr{p}}^2\right)\vctr{p}' - 2\vctr{p} \times \vctr{p}'}{1 + \norm{\sigma'}^2 \norm{\vctr{p}}^2 + 2\vctr{p}' \cdot \vctr{p}},
\end{equation}

\begin{equation} \label{eq:angle_error}
  \theta = 4 \tan^{-1} \left( \norm{\vctr{p}''} \right).
\end{equation}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\figmed]{obs_geom.png}
  \caption{Facet geometry including the observer direction $\unitv{o}$, Sun direction $\unitv{s}$, normal vector $\unitv{n}_i$, unshadowed area $\bar{a}_i$, shadowed area $\tilde{a}_i$, and counterclockwise vertex locations $\left\{ \vctr{v}_{i,1}, \vctr{v}_{i,2}, \vctr{v}_{i,3} \right\}$. }
  \label{fig:facet_geom}
\end{figure}

\begin{equation} \label{eq:us_area}
  \bar{a} = a - \sum_{d=1}^{n} \sum_{K \in \text{comb}(n,d)} (-1)^{d+1} A\left(\bigcap\limits_{k \in K} P_k\right).
\end{equation}

\begin{equation} \label{eq:brdf_blinn_phong}
  f_r(\unitv{s}, \unitv{o}) = \frac{C_d}{\pi} + \frac{n+2}{2\pi} \frac{C_s (\unitv{n} \cdot \unitv{h})^n}{4 (\unitv{n} \cdot \unitv{s})(\unitv{n} \cdot \unitv{o})}.
 \end{equation}

 \begin{equation} \label{eq:lc_norm}
  f_p(\unitv{s}_k, \unitv{o}_k) = \sum_{i=1}^n{\prf{B}\left[\bar{a}_i(\unitv{s}_k, \unitv{o}_k)
  f_{r,i}(\unitv{s}_k, \unitv{o}_k)
   (\unitv{n}_i \cdot \unitv{s}_k)
   (\unitv{n}_i \cdot \unitv{o}_k)
   \right]}. 
 \end{equation}

 \begin{equation} \label{eq:general_bright}
  \bar{S}_{\text{SO},k} = f_p(\unitv{s}_k, \unitv{o}_k) \frac{A \cdot \Delta t_k \cdot f_\odot(\vctr{r})}{g R_\oplus^2 r_k^2} \int_{0}^{\infty}{P(\lambda)Q(\lambda)T_k(\lambda) I_\odot(\lambda) \left(\frac{\lambda}{hc}\right)}\,d\lambda. 
\end{equation}

\begin{equation} \label{eq:sensor_noise}
  \sigma_\text{sensor} = \sqrt{n_\text{pix} \left( \Delta t \cdot \lambda_\text{dark} + \sigma_\text{read}^2 \right)}.
\end{equation}

\begin{equation}
  \sigma_\text{flat} = f_k \sqrt{\sum_{i=1}^{n_\text{pix}} S_i^2}.
\end{equation}

\begin{equation}
  \lambda_{\text{back},k} = n_{\text{pix},k} \left( \lambda_{\text{moon},k} + \lambda_{\text{star},k} + \lambda_{\text{twi},k} + \lambda_{\text{zod},k} + \lambda_{\text{star},k} + \lambda_{\text{poll},k} \right).
\end{equation}

\begin{equation} \label{eq:scint_noise}
  \sigma^2_{Y,k} = 10^{-6} D^{-4/3} (\Delta t)_k^{-1} \cos^{-3}\left(\gamma_k\right) e^{\frac{-2h_\text{obs}}{H}}.
\end{equation}

\begin{equation}
  \lambda_{\text{shot},k} = \frac{\bar{S}_{\text{SO},k}}{\sqrt{g}}.
\end{equation}

\begin{equation} \label{eq:sigma_total}
  \sigma^2_{S,k} = \lambda_{\text{back},k} + \bar{S}_{\text{SO},k} \sigma^2_{Y,k} + \lambda_{\text{shot},k} + \sigma^2_\text{flat},
\end{equation}

\begin{equation}
  S_{\text{SO},k} \sim \mathcal{N}\left( \bar{S}_{\text{SO},k}, \sigma^2_{S,k} \right).
 \end{equation}

 \begin{table}[ht]
  \centering
  \caption{Observation parameters 2}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  True inertia ratios $\begin{bmatrix}J_y / J_x & J_z / J_x\end{bmatrix}$ & $\begin{bmatrix} 1.0 & 0.5 \end{bmatrix}$ \\ \hline
  Initial simulation date & October 10, 2024 08:00:00.000 UTC \\ \hline
  Object identity (COSPAR ID) & 1987-084D \\ \hline 
 Light curve duration & $2$ minutes \\ \hline
 Measurement frequency & $0.5$ Hz \\ \hline
 Integration time & $0.01$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}

\begin{table}[ht]
  \centering
  \caption{Observation parameters 2}
  \vspace*{6pt}
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Variable} & \textbf{Value} \\ \hline
  True inertia ratios $\begin{bmatrix}J_y / J_x & J_z / J_x\end{bmatrix}$ & $\begin{bmatrix} 1.0 & 0.5 \end{bmatrix}$ \\ \hline
  Initial simulation date & October 10, 2024 08:00:00.000 UTC \\ \hline
  Object identity (COSPAR ID) & 1987-084D \\ \hline 
 Light curve duration & $2$ minutes \\ \hline
 Measurement frequency & $0.5$ Hz \\ \hline
 Integration time & $0.01$ seconds \\ \hline
  \end{tabular}
  \label{tb:case1_in}
\end{table}
